%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Tushar Makkar
\documentclass[margin,line]{resume}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[hidelinks,colorlinks,citecolor=Fuchsia,urlcolor=blue,linkcolor=Cerulean]{hyperref}
\hypersetup{
     colorlinks   = true,
     citecolor    = gray
}


%______________________________________________________________________________________________________________________
\begin{document}
\name{ \moveleft.9\hoffset\centerline{\large\bf \href{http://tusharmakkar08.github.io/}{TUSHAR MAKKAR}}}
\address { \centerline{Bengaluru, India $\bullet$ (+91) 9008751866 $\bullet$ tusharmakkar08@gmail.com}}

\begin{resume}

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \bf EDUCATION}

    
    {\bf Bachelor of Technology, Computer Engineering} \hfill   May 2015 \\
                      % \sl will be bold italic in New Century Schoolbook (or
                % any postscript font) and just slanted in
          %  Computer Modern (default) font
                \href{http://nitk.ac.in/}{National Institute of Technology, Surathkal, Karnataka, India} \\
		CGPA : {\bfseries 9.36/10.0}, Department Rank: {\bfseries 4/107}
               % Position in Class:1\\

  {\bf All India Senior Secondary School Examination (C.B.S.E) } \hfill   July 2011 \\
                      % \sl will be bold italic in New Century Schoolbook (or
                % any postscript font) and just slanted in
          %  Computer Modern (default) font
                \href{http://www.pkrjainpublicschool.com/}{P.K.R. Jain Sr. Sec. Public School, Ambala, Haryana, India} \\
		Percentage Secured : {\bfseries 95.6\%}, District Rank: {\bf1}

  {\bf All India Secondary School Examination (C.B.S.E)} \hfill   July 2009 \\
                      % \sl will be bold italic in New Century Schoolbook (or
                % any postscript font) and just slanted in
          %  Computer Modern (default) font
                \href{http://www.pkrjainpublicschool.com/}{P.K.R. Jain Sr. Sec. Public School, Ambala, Haryana, India} \\
		Percentage Secured : {\bfseries 98\%}, District Rank: {\bf 1}

            
    %__________________________________________________________________________________________________________________
    
     % Interests  
   % \section{\mysidestyle \bf INTERESTS \\ } 
   % {\bf } Algorithms, Data Structures, Data Science, Applied Mathematics and Statistics
    % Technical Skills
    \section{\mysidestyle \bf TECHNICAL \\ SKILLS} 
    {\bf Languages:} Python, C++, Java
    \\ {\bf Databases :} SQL, NoSQL
     \\ {\bf Operating System :} OS X, Linux (Debian/RPM), Windows
   
    %__________________________________________________________________________________________________________________
    % Experience
    \section{\mysidestyle \bf EXPERIENCE}
    {\bf SDE - II (Data Science), \href{https://www.vyom.com/}{Vyom}\href{https://www.rivigo.com/}{(Rivigo)}}\hfill March 2017- Present\\
      $\bullet$ Developed Pricing Engine. Pricing Engine enables Vyom to present best route price for transporters and supply side to ensure better return load efficiencies and more business for fleet owners/brokers using machine learning models.\\
  $\bullet$ Worked on building and architecting Vyom Rate Exchange (World's first truck freight exchange), User Reliability Engine and Ramanujan - An engine where different ML models compete to predict price on a given route.

{\bf SDE - II, \href{http://codenation.co.in/}{CodeNation}}\hfill June 2015- March 2017\\
      $\bullet$ Underwent through \href{https://hbr.org/2001/04/no-ordinary-boot-camp}{Trilogy University (TU'15)}\\
	$\bullet$ Proposed and Developed Library Suggestion Engine. Steered the project smoothly from requirement\linebreak gathering stage till production. \\
	$\bullet$ Used Machine Learning, NLP, AI, static and dynamic code analysis techniques. \emph{Patent} pending for the same.
    
      {\bf Software Engineering Intern/Researcher, \href{https://www.google.com/}{Google}}\hfill May 2014- July 2014\\
      $\bullet$ Worked on \href{https://en.wikipedia.org/wiki/Word-sense_disambiguation}{Word Sense Disambiguation} problem in \href{http://en.wikipedia.org/wiki/Ray_Kurzweil}{Ray Kurzweil's} \emph{Machine Intelligence Group}\linebreak under the guidance of \href{http://research.google.com/pubs/ShaileshKumar.html}{Shailesh Kumar}.\nolinebreak\\
	$\bullet$ Designed the algorithm for finding context of a word using Cooccurence data and WordNet. Implemented the framework for disambiguating the words and quantifying how good the \emph{WordNet} and \emph{Cooccurence} based classifier performs on a labelled \emph{SemCor} corpus .
    
     {\bf Software Engineering Intern/Researcher, \href{http://algorithmicinsight.com/}{Algorithmic Insight}}\hfill May 2013- July 2013\\
      $\bullet$ Worked on implementation, design and optimization of \emph{Least Cost Fulfillment Algorithm} which aimed at systemizing the order fulfillment process of \href{http://www.suppliesguys.com/}{The Supplies Group}, under the guidance of \href{https://www.linkedin.com/in/sarabjot-singh-a130711}{Sarabjot Singh}.

 {\bf Network Developer and Protocol Designer, \href{http://trestor.org/}{Trestor Foundation}}\hfill Jan 2014-Oct 2015\\
	$\bullet$ Worked on designing and establishing new true P2P cryptocurrency which will give better security, privacy, anonymity and transparency. \\
$\bullet$ Worked on developing network layer protocols, consensus algorithm, biometric authentication \linebreak system and web service API . 

    %__________________________________________________________________________________________________________________
    % Publications
\section{\mysidestyle \bf Publications} 
 {\bf\href{http://ieeexplore.ieee.org/document/7148513/?arnumber=7148513}{Software development using context aware searching of components in large repositories}}\hfill IEEE \\
Proposed a  new approach to locate software components from large component online open source repositories faster encompassing the techniques like context-aware browsing, Hidden Markov Models based ranking and semantic tagging.
\pagebreak\\
{\bf\href{http://link.springer.com/chapter/10.1007/978-981-10-0251-9_32}{Extended Game Theoretic Dirichlet Based Collaborative Intrusion Detection Systems}}\hfill Springer \\
Proposed a  new approach for making Intrusion Detection System more robust/secure using a unique mix of Dirichlet Distribution based collaborative trust model and Nash-Equilibrium based game theoretical model. 

    %__________________________________________________________________________________________________________________
    % Projects
\section{\mysidestyle \bf PROJECTS} 

 {\bf\href{https://github.com/alecthomas/voluptuous}{Voluptuous}}\hfill April 2016 \\
$\bullet$ Voluptuous, despite the name, is a Python data validation library. It is primarily intended for validating data coming into Python as JSON, YAML, etc. \\
$\bullet$ Part of 2-member core Voluptuous development team. It has 1000+ github stars and 50+ contributors.
\\\\{\bf\href{https://github.com/tusharmakkar08/Imagyy}{Imagyy}}\hfill Nov 2015 \\
$\bullet$ Tool for scraping public profile photos from various social netorks like Facebook, Instagram, Quora, LinkedIn etc.\\ 
$\bullet$ Top-50 in \href{https://news.ycombinator.com/show}{Hacker News} for more than 48 hours.
 
    %__________________________________________________________________________________________________________________
    % Awards and Achievements
  \section{\mysidestyle \bf AWARDS} 
  {\bf Competitive Programming } 
 \\$\bullet$ Ranked {\bfseries 3rd} among Indian teams in \href{http://www.ieee.org/membership_services/membership/students/competitions/xtreme/index.html}{IEEEXtreeme-7.0}
\\$\bullet$ Qualified for both \href{icpc.amrita.ac.in}{ACM ICPC Amritapuri regionals} and \href{http://acm.iitkgp.ac.in/}{ACM ICPC Kharagpur regionals}. My team ranked {\bfseries 24th} in {\emph ACM ICPC onsite regionals} .
    \\$\bullet$ {\bfseries All World Rank – 15} in \href{http://www.codechef.com/rankings/INST2013/}{Instruo-2013} held at Codechef 
\\$\bullet$ Solved 275+ problems in Spoj . Handle :  \href{http://www.spoj.com/users/tusharmakkar08/}{tusharmakkar08}
\\\\    {\bf Haryana Pratibha Samman Award   }
     \\$\bullet$ Recieved Haryana Pratibha Samman Award from Chief Minister of Haryana for securing {\bfseries AIR - 3} in High School Examination
\\\\ {\bf Performance in Olympiads/Hackathons } 
     \\$\bullet$ Winner of Hackathon \href{https://www.acadaccelerator.com/Home/Events}{Code.Fun.Do} organised by \href{http://www.microsoft.com/en-in/msidc/default.aspx}{Microsoft}.
\\$\bullet$ {\bfseries AIR - 1} in Holy Faith's National Talent Search Exam .
    \\$\bullet$ {\bfseries AIR - 21} in \href{http://www.sofworld.org/nso}{National Science Olympiad} 
    \\$\bullet$ Secured 93 percentile score in both International Maths Olympiad and National Cyber Olympiad
\\$\bullet$ Qualified NTSE Level -1
    \\ \\  {\bf IIT JEE and AIEEE  } 
     \\$\bullet$ Amongst the  Top-0.01\% (AIR - 6094) in IIT JEE 2011 and Top-0.003\% (AIR - 3076) in AIEEE 2011
\\\\ {\bf Merit Certificate} 
     \\$\bullet$ Received Merit Certificate from Director for being in Top-0.1\% in Class
     \\$\bullet$ Mentioned in \href{http://stackexchange.com/leagues/307/week/puzzling/2015-03-09}{Top New Puzzling Stack Exchange users}




    %__________________________________________________________________________________________________________________
    % Extra-curricular Activities
         
    \section{\mysidestyle \bf EXTRA-CURRICULAR \\ ACTIVITIES}             
 $\bullet$ {\it Convenor of \href{https://webclub-nitk.github.io/}{Web Enthusiasts Club}}, an elite group of Computer Enthusiasts at NITK. \\
 $\bullet$ {\it Microsoft Student Partner} \\
  $\bullet$ {\it Joint Head of NITK Codechef Campus Chapter}  \\
     $\bullet$ {\it Joint Convenor of Computer Committee in \href{http://www.nitk.ac.in/students-activities/engineer}{Engineer} 2014}, the technical fest of NITK. \\
     $\bullet$ {\it Executive Member NITK IEEE Student Branch and Amateur Astronomers Club (previously SGC)} \\
 $\bullet$ {\it Webcasting Volunteer for Election Commission of India} in the Dakshina Kannada Parliamentary Constituency for the General Election to Lok Sabha - 2014. \\ 
$\bullet$ {\it Teaching Volunteer} at \href{http://www.teachforindia.org/}{Teach For India}, \href{http://makeadiff.in/}{Make a Difference} and \href{https://www.nanakg.org/}{Guru Nanak Sewa Sansthan}. \\ 


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF
